Oregon_Wildfire_full

### 2017-03-02 r_scripts/oregon_clean.rmd
make new sentence

---
title: "Oregon_Wildfire_reduced"
author: "Jingyang Liu"
date: "February 15, 2017"
---

@@

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # 20 mins

@@

## The overall summary  of data set
72 variables in total.
```{r overall summary}
# Check data structure
# summary(oregon_df)
```

@@

>>>>

---
title: "Oregon_Wildfire_full"
author: "Jingyang Liu"
date: "February 15, 2017"
---

@@

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # about 20 mins

@@

## The overall summary  of data set
72 variables in total.

```{r overall summary}
# Check data structure
# summary(oregon_df)
```

@@

### Output html?
